The NIR Corn Data Set

### 2019-08-20 MSc Project/paper_writing/MSc_dissertation_hongwei.tex
fix the table

	\subsection{Number of Samples}
	\label{sec:Number of Samples}

	\subsection{Number of Components}
	\label{sec:Number of Components}

@@

	\subsection{Cross-Validation}
	\label{sec:Cross-Validation}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{llllllllllll}
		\hline
		\multirow{2}{*}{Paper} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{Pre-treatment}                                           & \multicolumn{2}{c}{Moisture}    & \multicolumn{2}{c}{Oil}         & \multicolumn{2}{c}{Protein}   & \multicolumn{2}{c}{Starch}    \\ \cline{5-12} 
		&                                                                     &                                                                            &                                                                          & RMSECV         & RMSEP          & RMSECV         & RMSEP          & RMSECV        & RMSEP         & RMSECV        & RMSEP         \\ \hline
		1                      & mp6                                                                 & 60                                                                         & None                                                                     &                & 0.1446034(10)  &                & 0.09225961(10) &               & 0.1400926(10) &               & 0.3436289(10) \\
		2                      & m5                                                                  & 64 5-fold                                                                  & None                                                                     & 0.01488358(10) & 0.02113168(10) &                &                &               &               &               &               \\
		3                      & m5                                                                  & 60                                                                         & SavitzkyGolay                                                            &                & 0.05628462(5)  &                & 0.03163213(12) &               & 0.1085697(6)  &               & 0.2371506(6)  \\
		4                      & m5                                                                  & 40                                                                         & Scale                                                                    &                & 0.05862355(12) &                & 0.3891674(14)  &               & 0.3554446(8)  &               & 0.3878001(9)  \\
		4                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4194983(12)  &                & 0.7190886(17)  &               & 0.3731878(8)  &               & 0.4980389(9)  \\
		5                      & mp5                                                                 & 40                                                                         & Scale                                                                    &                & 0.4023674(10)  &                &                &               &               &               &               \\
		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  &                &                & 0.08331678(7)  & 0.07401861(7)  &               &               & 0.3322749(7)  & 0.2890035(7)  \\
		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  &                &                & 0.06403154(7)  & 0.05660701(7)  &               &               & 0.2426438(7)  & 0.2287837(7)  \\
		6                      & m5                                                                  & 64 5-fold                                                                  & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} &                &                & 0.04751603(7)  & 0.03468245(7)  &               &               & 0.3216974(7)  & 0.3037632(7)  \\
		7                      & m5                                                                  & 60                                                                         & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} &                & 0.04043771(6)  &                & 0.04937681(10) &               & 0.1021954(7)  &               & 0.2630782(5)  \\
		8                      & m5                                                                  & 52                                                                         & Delete 75 , 77                                                           & 0.02177367(10) & 0.0197695(10)  & 0.06621319(10) & 0.05955603(10) & 0.1194857(10) & 0.1123115(10) & 0.2937006(10) & 0.2723313(10)
	\end{tabular}
\end{table}

@@

\begin{table}[]
	\begin{tabular}{lllllllll}
		\hline
		Paper & \begin{tabular}[c]{@{}l@{}}Data\\ set\end{tabular} & \begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular} & Pre-treatment                                                            & \begin{tabular}[c]{@{}l@{}}RMSECV/\\ RMSEP\end{tabular} & Moisture       & Oil            & Protein       & Starch        \\ \hline
		1     & mp6                                                & 60                                                        & None                                                                     & RMSEP                                                   & 0.1446034(10)  & 0.09225961(10) & 0.1400926(10) & 0.3436289(10) \\
		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSECV                                                  & 0.01488358(10) &                &               &               \\
		2     & m5                                                 & 64 5-fold                                                 & None                                                                     & RMSEP                                                   & 0.02113168(10) &                &               &               \\
		3     & m5                                                 & 60                                                        & SavitzkyGolay                                                            & RMSEP                                                   & 0.05628462(5)  & 0.03163213(12) & 0.1085697(6)  & 0.2371506(6)  \\
		4     & m5                                                 & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.05862355(12) & 0.3891674(14)  & 0.3554446(8)  & 0.3878001(9)  \\
		4     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4194983(12)  & 0.7190886(17)  & 0.3731878(8)  & 0.4980389(9)  \\
		5     & mp5                                                & 40                                                        & Scale                                                                    & RMSEP                                                   & 0.4023674(10)  &                &               &               \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSECV                                                  &                & 0.08331678(7)  &               & 0.3322749(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(0,2,13)\end{tabular}  & RMSEP                                                   &                & 0.07401861(7)  &               & 0.2890035(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSECV                                                  &                & 0.06403154(7)  &               & 0.2426438(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(1,2,13)\end{tabular}  & RMSEP                                                   &                & 0.05660701(7)  &               & 0.2287837(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(2,2,13)\end{tabular} & RMSECV                                                  &                & 0.04751603(7)  &               & 0.3216974(7)  \\
		6     & m5                                                 & 64 5-fold                                                 & \begin{tabular}[c]{@{}l@{}}savitzkyGolay\\ filler=(2,2,13)\end{tabular}  & RMSEP                                                   &                & 0.03468245(7)  &               & 0.3037632(7)  \\
		7     & m5                                                 & 60                                                        & \begin{tabular}[c]{@{}l@{}}savitzkyGolay \\ filler=(1,2,21)\end{tabular} & RMSECV                                                  & 0.04043771(6)  & 0.04937681(10) & 0.1021954(7)  & 0.2630782(5)  \\
		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSECV                                                  & 0.02177367(10) & 0.06621319(10) & 0.1194857(10) & 0.2937006(10) \\
		8     & m5                                                 & 52                                                        & Delete 75 , 77                                                           & RMSEP                                                   & 0.0197695(10)  & 0.05955603(10) & 0.1123115(10) & 0.2723313(10)
	\end{tabular}
\end{table}

@@

>>>>

	\begin{figure}[h]    % start of figure environment
	\centering           % put the graph(s) in the centre of the page (horizontally)
	\includegraphics[width=8.5cm, angle=0]{Number_of_loop_times_mp5-1.pdf}  % width changes size
	\vspace*{-0.25cm}    % manual adjustment of vertical spacing
	\caption{SD under different loop times}          % a meaningful caption
	\label{fig:looptimes}               % label for the figure
\end{figure}                        % end of figure environment

	\subsection{Number of samples}
	\label{sec:Number of Samples}

	\subsection{Number of components}
	\label{sec:Number of Components}

@@

	\subsection{Cross-validation}
	\label{sec:Cross-Validation}

@@

\begin{table}[]
	\begin{tabular}{ll}
		\hline
		Number & Paper's title \\ \hline
		1 & A Partial Least Squares‐Based Consensus Regression Method for the Analysis of Near‐Infrared Complex Spectral Data of Plant Samples \\
		2 & A strategy that iteratively retains informative variables for selecting optimal variable subset in multivariate calibration \\
		3 & Reduced PCR/PLSR models by subspace projections \\
		4 & Stability competitive adaptive reweighted sampling (SCARS) and its applications to multivariate calibration of NIR spectra \\
		5 & Cross-validation for the selection of spectral variables using the successive projections algorithm \\
		6 & A variable elimination method to improve the parsimony of MLR models using the successive projections algorithm \\
		7 & Pretreating near infrared spectra with fractional order Savitzky–Golay differentiation (FOSGD) \\
		8 & Using consensus interval partial least square in near infrared spectra analysis
	\end{tabular}

\label{tab:papers}
\end{table}

@@

Table \ref{tab:moisture} is the regression for moisture.
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{llllllllllllllll}
	\cline{1-13}
	\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Moisture} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
	\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
	1 & mp6 & None & 60(LOO) & 10 &  & 0.148(0.0213) &  &  & 0.159 &  &  & 0.139 &  &  &  \\
	2 & m5 & None & 64(5-fold) & 10 & 0.0152(0.000739) & 0.0202(0.00319) &  & 0.0149 & 0.0201 &  & 0.00026 & 0.00035 &  &  &  \\
	3 & m5 & Scale & 40(LOO) & 12 &  & 0.0231(0.00443) &  &  & 0.3506 &  &  & 0.3485 &  &  &  \\
	3 & mp5 & Scale & 40(LOO) & 12 &  & 0.159(0.0178) &  &  & 0.3506 &  &  & 0.3485 &  &  &  \\
	4 & mp5 & Scale & 40(LOO) & 10 &  & 0.405(0.0467) &  &  & 0.357 &  &  & 0.265 &  &  &  \\
	5 & m5 & SG(1,2,13) & 60(3-fold) & 5 &  & 0.0547(0.00942) &  &  & 0.040 &  &  & 0.012 &  &  &  \\
	6 & m5 & SG(1,2,21) & 60(LOO) & 6 &  & 0.0396(0.00625) &  &  & 0.045 &  &  & 0.019 &  &  &  \\
	8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0221(0.0018) & 0.0194(0.00298) &  & 0.0124 & 0.0157 &  & 0.0047 & 0.0056 &  &  & 
\end{tabular}

\caption{regression of moisture.The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
\label{tab:moisture}
\end{table}

@@

Table \ref{tab:oil} is the regression for Oil.
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]

	\begin{tabular}{llllllllllllllll}
		\cline{1-13}
		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Oil} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
		1 & mp6 & None & 60(LOO) & 10 &  & 0.0991(0.0161) &  &  & 0.107 &  &  & 0.0948 &  &  &  \\
		3 & m5 & Scale & 40(LOO) & 14 &  & 0.396(0.0665) &  &  & 0.6912 &  &  & 0.6902 &  &  &  \\
		3 & mp5 & Scale & 40(LOO) & 14 &  & 0.694(0.095) &  &  & 0.6912 &  &  & 0.6902 &  &  &  \\
		5 & m5 & SG(1,2,13) & 60(3-fold) & 12 &  & 0.0329(0.00672) &  &  & 0.029 &  &  & 0.022 &  &  &  \\
		6 & m5 & SG(1,2,21) & 60(LOO) & 10 &  & 0.0505(0.0103) &  &  & 0.028 &  &  & 0.030 &  &  &  \\
		7 & m5 & SG(0,2,13) & 64(5-fold) & 7 & 0.0827(0.00419) & 0.0716(0.0116) &  & 0.0729 & 0.0855 &  &  & 0.0400 &  &  &  \\
		7 & m5 & SG(1,2,13) & 64(5-fold) & 7 & 0.0639(0.00357) & 0.0548(0.012) &  & 0.0577 & 0.0682 &  & 0.0363 & 0.0400 &  &  &  \\
		7 & m5 & SG(2,2,13) & 64(5-fold) & 7 & 0.0480(0.00312) & 0.0368 (0.0088) &  & 0.0370 & 0.0397 &  & 0.0363 & 0.0400 &  &  &  \\
		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.0651(0.00662) & 0.0604(0.00876) &  & 0.0613 & 0.0673 &  & 0.0483 & 0.0546 &  &  & 
	\end{tabular}

\caption{regression of oil. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
\label{tab:oil}
\end{table}
    \end{landscape}

	\begin{landscape}
Table \ref{tab:protein} is the regression for protein.
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{llllllllllllllll}
		\cline{1-13}
		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Protein} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
		1 & mp6 & None & 60(LOO) & 10 &  & 0.141(0.0203) &  &  & 0.150 &  &  & 0.145 &  &  &  \\
		3 & m5 & Scale & 40(LOO) & 8 &  & 0.349(0.051) &  &  & 0.4466 &  &  & 0.4349 &  &  &  \\
		3 & mp5 & Scale & 40(LOO) & 8 &  & 0.37(0.0485) &  &  & 0.4466 &  &  & 0.4349 &  &  &  \\
		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.107(0.0195) &  &  & 0.119 &  &  & 0.040 &  &  &  \\
		6 & m5 & SG(1,2,21) & 60(LOO) & 7 &  & 0.102(0.0186) &  &  & 0.110 &  &  & 0.033 &  &  &  \\
		8 & m5 & Delete 75 , 77 & 52(LOO) & 13 & 0.119 ( 0.0155 ) & 0.11(0.0169) &  & 0.1080 & 0.1353 &  & 0.0429 & 0.0846 &  &  & 
	\end{tabular}

\caption{regression of protein. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
\label{tab:protein}
\end{table}

\begin{landscape}
Table \ref{tab:starch} is the regression for starch.
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{llllllllllllllll}
		\cline{1-13}
		\multicolumn{1}{c}{\multirow{2}{*}{Paper}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Data\\ set\end{tabular}}} & \multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}Pre-\\ treatment\end{tabular}}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Calibration\\ set\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of\\ Components\end{tabular}} & \multicolumn{2}{c}{Starch} &  & \multicolumn{2}{c}{PLS in papers} &  & \multicolumn{2}{c}{Developed method} &  &  &  \\ \cline{6-7} \cline{9-10} \cline{12-13}
		\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  & RMSECV & RMSEP &  &  &  \\ \cline{1-13}
		1 & mp6 & None & 60(LOO) & 10 &  & 0.35(0.056) &  &  & 0.370 &  &  & 0.358 &  &  &  \\
		3 & m5 & Scale & 40(LOO) & 9 &  & 0.393(0.0736) &  &  & 0.5010 &  &  & 0.4443 &  &  &  \\
		3 & mp5 & Scale & 40(LOO) & 9 &  & 0.513(0.0779) &  &  & 0.5010 &  &  & 0.4443 &  &  &  \\
		5 & m5 & SG(1,2,13) & 60(3-fold) & 6 &  & 0.239(0.0449) &  &  & 0.196 &  &  & 0.100 &  &  &  \\
		6 & m5 & SG(1,2,21) & 60(LOO) & 5 &  & 0.258(0.0453) &  &  & 0.228 &  &  & 0.101 &  &  &  \\
		7 & m5 & SG(0,2,13) & 64(5-fold) & 8 & 0.333(0.0226) & 0.283(0.0624) &  & 0.312 & 0.214 &  & 0.240 & 0.219 &  &  &  \\
		7 & m5 & SG(1,2,13) & 64(5-fold) & 8 & 0.2412(0.0171) & 0.221(0.049) &  & 0.248 & 0.221 &  & 0.240 & 0.219 &  &  &  \\
		7 & m5 & SG(2,2,13) & 64(5-fold) & 8 & 0.318(0.0252) & 0.302(0.061) &  & 0.347 & 0.228 &  & 0.240 & 0.219 &  &  &  \\
		8 & m5 & Delete 75 , 77 & 52(LOO) & 10 & 0.292(0.0312) & 0.282(0.043) &  & 0.2579 & 0.2356 &  & 0.1137 & 0.1188 &  &  & 
	\end{tabular}

\caption{regression of starch. The values in parentheses corresponds to the cross-validation type in calibration set and standard deviation in moisture.}
\label{tab:starch}
\end{table}
    \end{landscape}

	\subsection{Developed method significant test}
\label{sec: test}
